\begin{thebibliography}{9}

    \bibitem{what_is_sls_cloudflare} What is serverless
    \url{https://www.cloudflare.com/learning/serverless/what-is-serverless}

    % https://doi.org/10.1145%2F1496091.1496100    what is the cloud,
    \bibitem{cloud_computing_definition} A Break in the Clouds: Towards a Cloud
    Deﬁnition ....

    \bibitem{what_is_the_cloud} What is the cloud
    \url{https://www.cloudflare.com/learning/cloud/what-is-the-cloud/}

    \bibitem{iaas} What is IaaS
    \url{https://www.cloudflare.com/learning/cloud/what-is-iaas}

    \bibitem{paas} What is PaaS
    \url{https://www.cloudflare.com/learning/serverless/glossary/platform-as-a-service-paas}

    \bibitem{saas} What is SaaS
    \url{https://www.cloudflare.com/learning/cloud/what-is-saas}

    \bibitem{separation_of_concerns}  Dijkstra, Edsger W (1982).
    "On the role of scientific thought". Selected writings on Computing: A Personal
    Perspective. New York, NY, USA: Springer-Verlag. pp. 60–66. ISBN 0-387-90652-5.
    \url{https://www.cs.utexas.edu/users/EWD/transcriptions/EWD04xx/EWD447.html}

    \bibitem{sls_providers_comparison}
    Liang Wang, UW-Madison; Mengyuan Li and Yinqian Zhang, The Ohio State University,
    Thomas Ristenpart, Cornell Tech; Michael Swift, UW-Madison
    "Peeking Behind the Curtains of Serverless Platforms"
    ISBN 978-1-939133-02-1
    \url{https://www.usenix.org/conference/atc18/presentation/wang-liang}

    \bibitem{what_is_js} What is JavaScript
    \url{https://developer.mozilla.org/en-US/docs/Learn/JavaScript/First_steps/What_is_JavaScript}

    \bibitem{node_org} Node.js
    \url{https://nodejs.org/en}

    \bibitem{node_event_loop} Node.js Event Loop
    \url{https://nodejs.dev/learn/the-nodejs-event-loop}

    \bibitem{node_on_backend} Node.js on Backend
    \url{https://www.netguru.com/blog/node-js-backend}

    \bibitem{node_event_loop_2} Node.js Event Loop
    \url{https://www.geeksforgeeks.org/node-js-event-loop/}

    \bibitem{typescript_lang} TypeScript
    \url{https://www.typescriptlang.org/}

    \bibitem{typescript} TypeScript: What is it and when is it useful?
    \url{https://medium.com/front-end-weekly/typescript-what-is-it-when-is-it-useful-c4c41b5c4ae7}

    \bibitem{common_js} Eric Elliott (26 June 2014). Programming JavaScript Applications: Robust Web Architecture with Node, HTML5, and Modern JS Libraries. "O'Reilly Media, Inc.". pp. 87–. ISBN 978-1-4919-5027-2.
    \url{https://books.google.com/books?id=jUfnAwAAQBAJ&pg=PA87}

    \bibitem{json_iso} JSON data interchange syntax ISO
    \url{https://www.iso.org/standard/71616.html}

    \bibitem{npm_scoped_packages} Npm Scoped packages
    \url{https://docs.npmjs.com/creating-and-publishing-an-organization-scoped-package}

    \bibitem{github_issues} Mastering Issues
    \url{https://guides.github.com/features/issues}

    \bibitem{monorepo} From Monolith to Monorepo
    \url{https://medium.com/@brockreece/from-monolith-to-monorepo-19d78ffe9175}

    \bibitem{agile} Agile Manifesto
    \url{https://agilemanifesto.org/iso/it/principles.html}

    \bibitem{continuous_delivery} L. Chen, "Continuous Delivery: Huge Benefits, but Challenges Too," in IEEE Software, vol. 32, no. 2, pp. 50-54, Mar.-Apr. 2015, doi: 10.1109/MS.2015.27.
    \url{https://ieeexplore.ieee.org/document/7006384}

    % bibtex
    % @ARTICLE{7006384,  author={L. {Chen}},  journal={IEEE Software},   title={Continuous Delivery: Huge Benefits, but Challenges Too},   year={2015},  volume={32},  number={2},  pages={50-54},  doi={10.1109/MS.2015.27}}

    \bibitem{circle_ci_official} CircleCi Documentation
    \url{https://circleci.com/docs/2.0/about-circleci}

    \bibitem{aws_api_gateway_doc} API Gateway Lambda Authorizers
    \url{https://docs.aws.amazon.com/apigateway/latest/developerguide/apigateway-use-lambda-authorizer.html}

    \bibitem{react_js} React - A JavaScript library for building user interfaces
    \url{https://reactjs.org/}

    \bibitem{dom_standard} DOM Living Standard
    \url{https://dom.spec.whatwg.org/}

    \bibitem{ts_generics} Typescript - Generics
    \url{https://www.typescriptlang.org/docs/handbook/generics.html}

    \bibitem{sls_pro_cons} Serverless pros and cons
    \url{https://hackernoon.com/what-is-serverless-architecture-what-are-its-pros-and-cons-cc4b804022e9}

    \bibitem{sls_aws_doc} Serverless Framework Aws Guide
    \url{https://www.serverless.com/framework/docs/providers/aws/guide/intro}

    \bibitem{data_access_object} Data Access Object Pattern
    \url{https://www.oracle.com/java/technologies/dataaccessobject.html}

    \bibitem{spazio_alla_scuola} Spazio alla scuola
    \url{https://www.fondazioneagnelli.it/2020/07/17/spazio-alla-scuola}

    \bibitem{aws_doc_runtimes} Aws Lambda Environment
    \url{https://docs.aws.amazon.com/lambda/latest/dg/runtimes-context.html}

\end{thebibliography}
